\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[blue]{classic}
\moderncvhead{1}
\moderncvbody{1}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.9]{geometry}
\definecolor{linkcol}{rgb}{0,0.2,0.6}
\usepackage[unicode,colorlinks,breaklinks,urlcolor=linkcol,linkcolor=linkcol]{hyperref}
\setlength{\hintscolumnwidth}{4cm}

\firstname{Anastasia}
\familyname{Lyupa}
\address{Moscow, Russia}{}
\mobile{+7 915 061-53-50}
\email{anastasiya.lyupa@gmail.com}
\homepage{linkedin.com/in/anastasia-lyupa-27656680}

\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

\begin{document}
\maketitle

\section{Summary}
\cvitem {} {Skilled and results-oriented Software Engineer with more than 7 years of experience working in a variety of environments with a breadth of programs and technologies. Seeking the position of C++ Software Engineer.}
\section{Experience}
\cvitem {\large{Feb 2013 -- present}}{\large\textbf{Samsung Research Russia}}
\cventry
  {2021}
  {Software Engineer}
  {Platform Lab}
  {\newline Android runtime and compiler optimization, decreasing application launch time. Working with existing code, feature development, bug fixing, shell scripting, adding Google unit tests to project}
  {\newline Tech stack: C++, Linux, AOSP}
  {}
\cventry
  {2020}
  {Project Leader}
  {Sensor Data Part}
  {\newline Development of a sensors simulation for robots. Communication with customers / stack holders, planning, tasks distribution, preparation of project documentation, feature development, bug fixing}
  {\newline Tech stack: C++, Unreal Engine 4}
  {}
\cventry
  {2019}
  {Software Engineer}
  {Sensor Data Part}
  {\newline Development of a simulator for Robot Vacuum Cleaner. Design and implementation of map editor mode for the simulator}
  {\newline Tech stack: C++, Unreal Engine 4}
  {}
\cventry
  {2018}
  {Software Engineer}
  {AI Tools Lab}
  {\newline Development of a tool for combining several repositories into firmware. Working with existing code, feature development, bug fixing, setting up and maintaining CI}
  {\newline Tech stack: Python}
  {\url{https://github.com/Samsung/combirepo}}
\cventry
  {2017}
  {Software Engineer}
  {SW Tools Lab}
  {\newline Investigating issues in Tizen OS with ASan, SVACE, Valgrind. Static code analysis, memory profiling, fixing issues in system libraries, preparation of reports and documentation}
  {\newline Tech stack: C/C++, Linux}
  {\url{https://www.tizen.org/}}
\cventry
  {2016}
  {Maternity leave}
  {}
  {}
  {}
  {}
\cventry
  {2013 -- 2015}
  {Junior Software Engineer}
  {Tizen Platform Lab}
  {\newline Low level profiling tool development for Tizen OS which became a part of Tizen Studio. Working with Tizen Studio, feature development, bug fixing and optimization, testing on devices and emulators}
  {\newline Tech stack: C, Linux}
  {\url{https://www.tizen.org/}}

\newpage

\section{Skills}
\cvitem{Programming Languages}{C, C++, Python}
\cvitem{IDE/Build systems}{Visual Studio, Eclipse, CMake, Soong}
\cvitem{CI}{Git, Gerrit, Jenkins, Docker}
\cvitem{Documentation}{Latex, Markdown}

\section{Education}
  \cventry
    {2014 -- 2019}
    {Computer Science and Computer Engineering}
    {Moscow Institute of Physics and Technology}
    {Department of Control and Applied Mathematics}
    {Postgraduate education, Reseacher}{}
  \cventry
    {2012 -- 2014}
    {Applied Mathematics and Physics}
    {Moscow Institute of Physics and Technology}
    {Department of Control and Applied Mathematics}
    {Master's degree}
    {GPA 4.8}
  \cventry
    {2008 -- 2012}
    {Applied Mathematics and Physics}
    {Moscow Institute of Physics and Technology}
    {Department of Control and Applied Mathematics}
    {Bachelor's degree}
    {GPA 4.8}

\section{Research}
\cvitem{}{My research topic is multiphase flow simulation.
Publications are listed in my Research Gate profile.
Some of them are indexed by Scopus and Web of Science.}
\cvitem{Research Gate}{\url{https://www.researchgate.net/profile/Anastasia_Lyupa/publications}}
\cvitem{Project}{\url{https://github.com/alyupa/multiphase-flow-modeling}}

\section{Languages}
\cvitem {Russian}{Native}
\cvitem {English}{Upper-Intermediate}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

